Effects of the body force on the evacuation dynamics

### 2019-12-20 paper.tex
Update paper.tex

>>>>

The complex behavior of pedestrians feature either his (her) feelings and 
the environmental conditions. The former is expressed, for example, by his 
(her) moving ``attitude'' (say, self-assuredness). The latter brings out the 
observed separation between pedestrians. Also, the ``contacts'' between 
individuals address some kind of ``unwanted'' slowing down. All these 
observed patterns are commonly quantified in the literature into a a set of 
characteristic  parameters. The experimental meaning of these parameters is as 
follows.

\begin{itemize}
\item[(i)] The walking attitude of a pedestrian may appear somewhat 
``assertive'' if he (she) reacts actively to unexpected behaviors 
\cite{lakoba_2005,helbing_1995}. The smaller the reaction time, the more 
assertive or aggresive observed posture. The associated parameter to this 
behavior is the relaxation or characteristic time $\tau$ 
\cite{johansson_2009,helbing_2000}.

\item[(ii)] Despite the reactive attitude $\tau$, the pedestrian addresses a 
``free'' (undisturbed) walking speed $\v_0$. This speed expresses his (her) 
motivation or intention to reach a certain destination (as comfortable as 
possible). Observations commonly associate $0.6\,$m/s, $1\,$m/s or $1.5\,$m/s 
to relaxed, normal or nervous walking speeds, respectively  
\cite{helbing_1995,helbing_2000,li_2015}.

\item[(iii)] The walking speed of pedestrians appears to be lower in a 
crowded walkway with respect to their usually expected ``free'' walking speeds 
\cite{weidmann_1992,lakoba_2005}. Pedestrians tend to reduce their speed within 
crowded environments because they perceive not enough space for taking a 
step  \cite{johansson_2009}. This (perceived) step distance is therefore an 
influential parameter on the pedestrians behavior. It is known as the 
characteristic length $B$.

\item[(iv)] Physical interactions occur in very crowded environments. The 
``body force''  and ``sliding friction'' can be introduced straight forward. 
This will be done in Section \ref{background}. But it is worth noting that 
both are associated to the moving difficulties (say, slowing down and 
obstructions) observed in contacting pedestrians.

\end{itemize}

Table~\ref{table_data} shows a few empirical figures for the most common 
parameters. More data is available throughout the literature (see, for example, 
Refs.~\cite{hoogendoorn_2007,seyfried_2007,johansson_2007,moussaid_2009,
luber_2010,seer_2014,li_2015} ). We intentionally omitted data that assumes a 
specific mathematical model. The exhibited values should also be considered as a 
general purpose approach, since no distinction has been made on age, gender or 
cultural habits. \\

\begin{table}
\begin{tabular}{cccccc}
 \hline
 $\tau$[s]   & $m$[kg]     & $v_d$[m/s]  &  $B$[m]  & $k$[kg/s$^2$] &  Refs. \\
 \hline
0.61         & ---         & 1.24 & $0.36+1.06\,v$ &  ---                 &  
 \cite{seyfried_2007} \\
0.50$^*$     & 80$^*$      & 1.34 & 0.50           &  ---                 &  
\cite{weidmann_1992,lakoba_2005}\\
---          & $67.5$      & 1.39 &  ---           &  $96.1 + 12694.1\,x$ & 
\cite{song_2019}\\
---          & $67.0$      & 1.39 &  ---           &  $97.0 + 29378.9\,x$ & 
\cite{song_2019}\\

\hline
\end{tabular}
\caption{The experimental data for the pedestrian parameters, as explained in 
Section~\ref{experimental}. The magnitude $v$ means de pedestrian velocity 
(m/s). The magnitude $x$ means the compression length (m). The upper row for 
Ref.~\cite{song_2019} corresponds data acquired in winter and the lower row to 
datas acquiquired in summer. The asterisk ($^*$) corresponds to reasonable 
estimates. }
\label{table_data}
\end{table}

A first examination of the figures in Table~\ref{table_data} shows that the 
choise $\tau\simeq0.6\,$s seems to be a reasonable estimation for the 
relaxation time, although this may vary with respect to gender or culture 
\cite{siddharth_2018}. Additionally, we confirm that normal pedestrians attain 
desired velocties around $1.3\,$m/s. \\

No body contacts were reported in Refs.~\cite{seyfried_2007,weidmann_1992} 
since these experiments correspond to the low density regime. At this instance, 
the pedestrian does not feel to be too close to the others....    \\
